Making all equalities equal

### 2021-09-23 paper.lagda.tex
refactored the code

      in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
  eqsEqual _≣₁_ _≣₂_ ⦃ eq ≣-≡-≡₁ ⦄ ⦃ eq ≣-≡-≡₂ ⦄ = ≣-≡-≡₁ ∙ sym ≣-≡-≡₂
\end{code}

@@

\begin{code}
module _ {a} {A : Set a} where
  instance
    ≡-IsEquality : IsEquality {A = A} _≡_
    ≡-IsEquality = eq refl
  ≡-Equality : Equality {_} {a} {A}
  ≡-Equality = eqC _≡_

@@

\begin{code}
  instance
    ≡p-IsEquality : IsEquality {A = A} _≡p_
    ≡p-IsEquality = sym-Equality p-c
\end{code}

@@

\begin{code}
  instance
    ≃-IsEquality : IsEquality
      {A = Type ℓ} _≃_
    ≃-IsEquality = sym-Equality univalencePath'
\end{code}

@@

  instance
    ≐-IsEquality : IsEquality {A = A} _≐_
    ≐-IsEquality = eq λ {x} {y} → ≐≡≡ ∙
      λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i
\end{code}

@@

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  ≣-Type' = ≣-Type {a} {ℓ} {A}
  ℓ₁ = ℓ-max a ℓ

  module _
    (_≡₁_ : ≣-Type')
    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
    where

@@

      instance
        isEquality : IsEquality _≣_
        isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)

    module _
      (_≡₂_ : ≣-Type')
      ⦃ eq₂ : IsEquality _≡₂_ ⦄
      where

@@

    module _
      (_≡₃_ : ≣-Type {ℓ-suc ℓ₁} {a})
      ⦃ eq₃ : IsEquality _≡₃_ ⦄
      where

@@

        instance
          isEquality₂ : IsEquality₂ _≣_
          isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)

          isEquality : IsEquality _≣_
          isEquality = eq (IsEquality₂.≣-≡-≡ isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)

        ≡-≡-≣ : {x y : A} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ isEquality
          in transport α₁ (α₂ ∙ α₃)

      module _
        (_≡₂_ : ≣-Type')
        ⦃ eq₂ : IsEquality _≡₂_ ⦄
        where

        instance
          ≡₂-Equality₃ : IsEquality₃ _≡₂_
          ≡₂-Equality₃ = eq α
            where
              open IsEquality eq₃
              α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ _≡₂_))

@@

  leibniz : IsEquality _≐_
  leibniz =
    IsEquality₂.isEquality (eq FinalEquality.≐≡≡)

>>>>

      in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
  eqsEqual _ _ ⦃ eq ≣-≡-≡₁ ⦄ ⦃ eq ≣-≡-≡₂ ⦄ = ≣-≡-≡₁ ∙ sym ≣-≡-≡₂
\end{code}

@@

\begin{code}
module _ {a} {A : Set a} where
  instance
    ≡-IsEquality : IsEquality {A = A} _≡_
    ≡-IsEquality = eq refl
  ≡-Equality : Equality {ℓ = a}
  ≡-Equality = eqC _≡_

@@

\begin{code}
  instance
    ≡p-IsEquality : IsEquality {A = A} _≡p_
    ≡p-IsEquality = sym-Equality p-c
  ≡p-Equality : Equality {ℓ = a}
  ≡p-Equality = eqC _≡p_
\end{code}

@@

\begin{code}
  instance
    ≃-IsEquality : IsEquality
      {A = Type ℓ} _≃_
    ≃-IsEquality = sym-Equality univalencePath'
  ≃-Equality : Equality {ℓ = ℓ}
  ≃-Equality = eqC _≃_
\end{code}

@@

  instance
    ≐-IsEquality : IsEquality {A = A} _≐_
    ≐-IsEquality = eq λ {x} {y} → ≐≡≡ ∙
      λ i → ≡p-IsEquality {ℓ-zero} .≣-≡-≡ {x} {y} i

  ≐-Equality : Equality {ℓ = ℓ-suc ℓ-zero}
  ≐-Equality = eqC _≐_
\end{code}

@@

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  private
    ≣-Type' = ≣-Type {a} {ℓ} {A}
    ℓ₁ = ℓ-max a ℓ

  module _
    (Eq₁ : Equality {_} {ℓ} {A})
    where

    open Equality Eq₁ renaming (_≣_ to _≡₁_; isEquality to eq₁)

@@

      instance
        ≣-isEquality : IsEquality _≣_
        ≣-isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)

    module _
      (Eq₂ : Equality {_} {ℓ} {A})
      where

      open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)

@@

    module _
      (Eq₃ : Equality {A = Set ℓ₁})
      where

      open Equality Eq₃ renaming (_≣_ to _≡₃_; isEquality to eq₃)

@@

        instance
          ≣-isEquality₂ : IsEquality₂ _≣_
          ≣-isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)

          ≣-isEquality : IsEquality _≣_
          ≣-isEquality = eq (IsEquality₂.≣-≡-≡ ≣-isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)

        ≡-≡-≣ : {x y : A} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y
        ≡-≡-≣ = let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = IsEquality.≣-≡-≡ eq₁
          α₃ = IsEquality.≡-≡-≣ ≣-isEquality
          in transport α₁ (α₂ ∙ α₃)

      module _
        (Eq₂ : Equality {_} {ℓ} {A})
        where

        open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)

        instance
          ≡₂-Equality₃ : IsEquality₃ _≡₂_
          ≡₂-Equality₃ = eq α
            where
              open IsEquality eq₃
              α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ (eqC _≡₂_)))

@@

  leibniz : IsEquality {A = A} _≐_
  leibniz =
    IsEquality₂.≣-isEquality {Eq₁ = eqC _≡p_} (eq FinalEquality.≐≡≡)
